Election 2024

### 2024-11-03 paper/paper.qmd
Discussion section addtions

plt.figure(figsize=(18, 14))
plt.step(x, cumulative_votes, where='post', color='navy', linewidth=2, marker='o')
x_reversed = np.flip(x)
plt.step(x_reversed, cumulative_votes_reversed, where='post', color='red', linewidth=2, marker='o')

@@

@@

## What Else Do We Learn About the World?

@@

Candidate Trump’s low likelihood of winning shown by our results may under-represent his support, this claim is supported by the disparity with the betting markets. This could be a result of a common problem with polling data, response rate bias. In the previous two elections, where Donald Trump was also the republican candidate, his polling was far below the eventual results on election day. Post-mortems of both elections indicated evidence of those supporting Trump not participating in polls and thus under-presenting Republican support [@clinton2021task, @kennedy2018evaluation]. Should this trend continue, and be present in the polls used in this analysis, it may be expected that Trump could surprise the model and win some of these swing states. Another reason Trump could outperform the model is another bias often seen in surveys, one of social desirability. Trump is a unique candidate as, if elected, he would become the first president to be elected with federal crime conviction. This along with other negative publicity the former host of tv’s apprentice has garnered since the start of his political campaign could bias voters from publicly or privately showing their support. Even with the quality polls used in this analysis, where steps are taken to ensure representative results (see appendix B), we could be observing a skew in the results.
Another aspect that

>>>>

plt.figure(figsize=(20, 14))
plt.step(x, cumulative_votes, where='post', color='navy', linewidth=2, marker='o')
x_reversed = np.flip(x)
plt.step(x_reversed, cumulative_votes_reversed, where='post', color='red', linewidth=2, marker='o')

@@

The result of the model tells us that overall the polls in october are favouringh Harris to win the election. From th perpctiv of the republican party if they wish to "turn the tide" this model highlights which of the swing states are more possible to flip than others. North Carolina is the premier state predicted to go blue with the highest liklyhood of Trump winning. It would be recommended to allocate resources here to try and win a state from Harris. As far as retaining currently favoured states, Michigan is a weak position for Trump according to the model, nearing a coin flip. As this state holds 15 lectoral college votes, 4th most of the swing states, it is a key state to win. Assuming the model's correct prediction that Michigan is currently held by Trump, expect the democrats to attempt to tip the scales in their favor here.

@@

@@

Candidate Trump’s low likelihood of winning shown by our results may under-represent his support, this claim is supported by the disparity with the betting markets. This could be a result of a common problem with polling data, response rate bias. In the previous two elections, where Donald Trump was also the republican candidate, his polling was far below the eventual results on election day. Post-mortems of both elections indicated evidence of those supporting Trump not participating in polls and thus under-presenting Republican support (@clinton2021task , @kennedy2018evaluation). Should this trend continue, and be present in the polls used in this analysis, it may be expected that Trump could surprise the model and win some of these swing states. Another reason Trump could outperform the model is another bias often seen in surveys, one of social desirability. Trump is a unique candidate as, if elected, he would become the first president to be elected with federal crime conviction. This along with other negative publicity the former host of tv’s apprentice has garnered since the start of his political campaign could bias voters from publicly or privately showing their support. Even with the quality polls used in this analysis, where steps are taken to ensure representative results (see appendix B), we could be observing a skew in the results.
Another aspect that
